---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# Rsrat

Rsrat provides the package to evalute the software reliability from the fault data collected in the testing phase. Rsrat can use two types of data; fault-detection time data and its grouped data. The fault-detection time data is a sequence of time intervals of fault detection times (CPU time, etc). Also its grouped data is a sequence of the number of detected faults for each time interval (per a working day, per a week, etc). The reliability evaluation is based on the software reliability growth model with NHPP (non-homogeneous Poisson process). 

## Installation

You can install Rsrat from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("okamumu/Rsrat")
```

## Example

This is an example of the estimation of software reliability growth models from a fault data (tohma). 

```{r example1}
### load library
library(Rsrat)

### load example data
data(dacs)

### tohma is a grouped data
tohma

### Esimate all models and select the best one in terms of AIC
(result <- fit.srm.nhpp(fault=tohma))

### Draw the graph 
mvfplot(fault=tohma, mvf=list(result$srm))
```

The second example illustrates the estimation for two specified models.

```{r example2}
### All models in the package
srm.models

### Estimate two models and no select
(result <- fit.srm.nhpp(fault=tohma, srm.names=c("exp", "gamma"), selection=NULL))

### Draw the graph
mvfplot(fault=tohma, mvf=lapply(result, function(m) m$srm))
```
